---
title: "AK dashboard"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = F)
```

```{r}
if (!require("librarian")){
  install.packages("librarian")
  library(librarian)
}
shelf(
  dplyr, dygraphs, DT, flexdashboard, glue, here, readr)
```

# Eastern Bering Sea

```{r, child='_child_ebs.Rmd'}
```

# Western AI


### Least Auklet reproductive success

```{r}
read_csv("/Users/bbest/github/bbest/r3-exercises/data/alaska/WAI_Least.csv") %>% 
  dygraph(xlab = "Year", group = "sync")
```


### Crested Auklet reproductive success

```{r}
read_csv("/Users/bbest/github/bbest/r3-exercises/data/alaska/WAI_Crest.csv") %>% 
  dygraph(xlab = "Year", group = "sync")
```


### Ammodytes in Tufted Puffin diet

```{r}
read_csv("/Users/bbest/github/bbest/r3-exercises/data/alaska/WAI_PSL.csv") %>% 
  dygraph(xlab = "Year", group = "sync")
```


### Gadids in Tufted Puffin diet

```{r}
read_csv("/Users/bbest/github/bbest/r3-exercises/data/alaska/WAI_Gad.csv") %>% 
  dygraph(xlab = "Year", group = "sync")
```


### Hexagrammids in Tufted Puffin diet

```{r}
read_csv("/Users/bbest/github/bbest/r3-exercises/data/alaska/WAI_Hex.csv") %>% 
  dygraph(xlab = "Year", group = "sync")
```


### Pelagic forager biomass

```{r}
read_csv("/Users/bbest/github/bbest/r3-exercises/data/alaska/WAI_Pelagic.csv") %>% 
  dygraph(xlab = "Year", group = "sync")
```


### Apex predator biomass

```{r}
read_csv("/Users/bbest/github/bbest/r3-exercises/data/alaska/WAI_Apex.csv") %>% 
  dygraph(xlab = "Year", group = "sync")
```


### Otters at Attu

```{r}
read_csv("/Users/bbest/github/bbest/r3-exercises/data/alaska/WAI_Ott.csv") %>% 
  dygraph(xlab = "Year", group = "sync")
```


### SSL non pup counts

```{r}
read_csv("/Users/bbest/github/bbest/r3-exercises/data/alaska/WAI_SSL.csv") %>% 
  dygraph(xlab = "Year", group = "sync")
```


### Habitat Impacted by Trawls

```{r}
read_csv("/Users/bbest/github/bbest/r3-exercises/data/alaska/WAI_Trawl.csv") %>% 
  dygraph(xlab = "Year", group = "sync")
```


# Central AI


### Pelagic forager biomass

```{r}
read_csv("/Users/bbest/github/bbest/r3-exercises/data/alaska/CAI_Pelagic.csv") %>% 
  dygraph(xlab = "Year", group = "sync")
```


### Apex predator biomass

```{r}
read_csv("/Users/bbest/github/bbest/r3-exercises/data/alaska/CAI_Apex.csv") %>% 
  dygraph(xlab = "Year", group = "sync")
```


### Otters at Amchitka

```{r}
read_csv("/Users/bbest/github/bbest/r3-exercises/data/alaska/CAI_Ott.csv") %>% 
  dygraph(xlab = "Year", group = "sync")
```


### SSL non pup counts

```{r}
read_csv("/Users/bbest/github/bbest/r3-exercises/data/alaska/CAI_SSL.csv") %>% 
  dygraph(xlab = "Year", group = "sync")
```


### School Enrollment

```{r}
read_csv("/Users/bbest/github/bbest/r3-exercises/data/alaska/CAI_School.csv") %>% 
  dygraph(xlab = "Year", group = "sync")
```


### Habitat Impacted by Trawls

```{r}
read_csv("/Users/bbest/github/bbest/r3-exercises/data/alaska/CAI_Trawl.csv") %>% 
  dygraph(xlab = "Year", group = "sync")
```


# Eastern AI


### Ammodytes in Tufted Puffin diet

```{r}
read_csv("/Users/bbest/github/bbest/r3-exercises/data/alaska/EAI_PSL.csv") %>% 
  dygraph(xlab = "Year", group = "sync")
```


### Gadids in Tufted Puffin diet

```{r}
read_csv("/Users/bbest/github/bbest/r3-exercises/data/alaska/EAI_Gad.csv") %>% 
  dygraph(xlab = "Year", group = "sync")
```


### Hexagrammids in Tufted Puffin diet

```{r}
read_csv("/Users/bbest/github/bbest/r3-exercises/data/alaska/EAI_Hex.csv") %>% 
  dygraph(xlab = "Year", group = "sync")
```


### Pelagic forager biomass

```{r}
read_csv("/Users/bbest/github/bbest/r3-exercises/data/alaska/EAI_Pelagic.csv") %>% 
  dygraph(xlab = "Year", group = "sync")
```


### Apex predator biomass

```{r}
read_csv("/Users/bbest/github/bbest/r3-exercises/data/alaska/EAI_Apex.csv") %>% 
  dygraph(xlab = "Year", group = "sync")
```


### SSL non pup counts

```{r}
read_csv("/Users/bbest/github/bbest/r3-exercises/data/alaska/EAI_SSL.csv") %>% 
  dygraph(xlab = "Year", group = "sync")
```


### School Enrollment

```{r}
read_csv("/Users/bbest/github/bbest/r3-exercises/data/alaska/EAI_School.csv") %>% 
  dygraph(xlab = "Year", group = "sync")
```


### Habitat Impacted by Trawls

```{r}
read_csv("/Users/bbest/github/bbest/r3-exercises/data/alaska/EAI_Trawl.csv") %>% 
  dygraph(xlab = "Year", group = "sync")
```


# Western Gulf of Alaska


### Pacific Decadal Oscillation winter

```{r}
read_csv("/Users/bbest/github/bbest/r3-exercises/data/alaska/WGOA_PDO.csv") %>% 
  dygraph(xlab = "Year", group = "sync")
```


### SST Jun-Aug

```{r}
read_csv("/Users/bbest/github/bbest/r3-exercises/data/alaska/WGOA_SST.csv") %>% 
  dygraph(xlab = "Year", group = "sync")
```


### Mesoplankton Biomass

```{r}
read_csv("/Users/bbest/github/bbest/r3-exercises/data/alaska/WGOA_Meso.csv") %>% 
  dygraph(xlab = "Year", group = "sync")
```


### Copepod Community Size

```{r}
read_csv("/Users/bbest/github/bbest/r3-exercises/data/alaska/WGOA_Cope.csv") %>% 
  dygraph(xlab = "Year", group = "sync")
```


### Motile Epifauna Biomass

```{r}
read_csv("/Users/bbest/github/bbest/r3-exercises/data/alaska/WGOA_Epi.csv") %>% 
  dygraph(xlab = "Year", group = "sync")
```


### Capelin(puffins)

```{r}
read_csv("/Users/bbest/github/bbest/r3-exercises/data/alaska/WGOA_Capelin.csv") %>% 
  dygraph(xlab = "Year", group = "sync")
```


### Apex Fish Biomass

```{r}
read_csv("/Users/bbest/github/bbest/r3-exercises/data/alaska/WGOA_Apex.csv") %>% 
  dygraph(xlab = "Year", group = "sync")
```


### Black-legged Kittiwake Reproductive Success

```{r}
read_csv("/Users/bbest/github/bbest/r3-exercises/data/alaska/WGOA_Blk.csv") %>% 
  dygraph(xlab = "Year", group = "sync")
```


### Stellar Sea Lion Non-pups

```{r}
read_csv("/Users/bbest/github/bbest/r3-exercises/data/alaska/WGOA_SSL.csv") %>% 
  dygraph(xlab = "Year", group = "sync")
```


### Human Population

```{r}
read_csv("/Users/bbest/github/bbest/r3-exercises/data/alaska/WGOA_Human.csv") %>% 
  dygraph(xlab = "Year", group = "sync")
```


# Eastern Gulf of Alaska


### Multivariate ENSO index (MEI DecJan)

```{r}
read_csv("/Users/bbest/github/bbest/r3-exercises/data/alaska/EGOA_ENSO.csv") %>% 
  dygraph(xlab = "Year", group = "sync")
```


### SST Jun-Aug

```{r}
read_csv("/Users/bbest/github/bbest/r3-exercises/data/alaska/EGOA_SST.csv") %>% 
  dygraph(xlab = "Year", group = "sync")
```


### Zooplankton Density Icy Strait (#/m3)

```{r}
read_csv("/Users/bbest/github/bbest/r3-exercises/data/alaska/EGOA_Zoop.csv") %>% 
  dygraph(xlab = "Year", group = "sync")
```


### Copepod Community Size

```{r}
read_csv("/Users/bbest/github/bbest/r3-exercises/data/alaska/EGOA_Cope.csv") %>% 
  dygraph(xlab = "Year", group = "sync")
```


### Motile Epifauna Biomass

```{r}
read_csv("/Users/bbest/github/bbest/r3-exercises/data/alaska/EGOA_Epi.csv") %>% 
  dygraph(xlab = "Year", group = "sync")
```


### SE Alaska Herring Mature Biomass

```{r}
read_csv("/Users/bbest/github/bbest/r3-exercises/data/alaska/EGOA_Herring.csv") %>% 
  dygraph(xlab = "Year", group = "sync")
```


### Apex Fish Biomass

```{r}
read_csv("/Users/bbest/github/bbest/r3-exercises/data/alaska/EGOA_Apex.csv") %>% 
  dygraph(xlab = "Year", group = "sync")
```


### Rhinoceros Auklet Chick Growth

```{r}
read_csv("/Users/bbest/github/bbest/r3-exercises/data/alaska/EGOA_Auk.csv") %>% 
  dygraph(xlab = "Year", group = "sync")
```


### Stellar Sea Lion Non-pups

```{r}
read_csv("/Users/bbest/github/bbest/r3-exercises/data/alaska/EGOA_SSL.csv") %>% 
  dygraph(xlab = "Year", group = "sync")
```


### Human Population

```{r}
read_csv("/Users/bbest/github/bbest/r3-exercises/data/alaska/EGOA_Human.csv") %>% 
  dygraph(xlab = "Year", group = "sync")
```

